Hrvatska u kontekstu europskih konvergencijskih klubova

### 2024-08-28 Paper.Rmd
los

```{r libs,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
#### LIBS ----
library(eurostat)
library(tidyverse)
library(zoo)
library(scales)
library(tseries)
library(urca)
library(fracdiff)
library(arfima)
library(gt)

@@

```{r data, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}

@@

```{r vizualizacija, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
# Define a custom date labeling function
quarterly_labels <- function(x) {
  format(x, "%Yq%q")
}

@@

```{r vizualizacija1, echo=FALSE, warning=FALSE, message=FALSE,, fig.width=10, fig.height=10}
# Print the plot
print(plot_combined_graph)

>>>>

```{r libs,  echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
#### LIBS ----
library(eurostat)
library(tidyverse)
library(zoo)
library(scales)
library(tseries)
library(urca)
library(fracdiff)
library(arfima)
library(gt)

@@

```{r data, echo=FALSE, message=FALSE, warning=FALSE,  results='hide'}

@@

```{r vizualizacija, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, results='hide'}
# Define a custom date labeling function
quarterly_labels <- function(x) {
  format(x, "%Yq%q")
}

@@

```{r vizualizacija1, echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=10}
# Print the plot
print(plot_combined_graph)
